Pulsar Classification using Deep Neural Networks

### 2018-04-22 paper/paper.tex
Started assembling the paper. The classification was done a while ago but this was delayed due to senior design.

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting instructions for NIPS 2017}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Kyle W.~MacMillan\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2017}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2017/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2017 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. This does not include acknowledgments and 
cited references which are allowed on subsequent pages.
Papers that exceed these limits will not be reviewed, or in any
other way considered for presentation at the conference.

The margins in 2017 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}

\title{Pulsar Classification using Deep Neural Networks}

\author{
  Kyle W.~MacMillan
  Department of Computer Science\\
  South Dakota School of Mines and Technology\\
  Rapid City, SD 57701 \\
  \texttt{kyle.macmillan@mines.sdsmt.edu} \\
}

\begin{document}

@@

\begin{abstract}
  Pulsars are rapidly rotating, highly magnetized, neutron stars and white 
  dwarfs that emit focused electromagnetic radiation in a beam. The beam is 
  only visible to us when it is directly facing Earth and is the reason for 
  their pulsed nature. This paper approaches classification of pulsars and 
  non-pulsars with the intent of learning more about TensorFlow. The 
  classification method used is Deep Neural Networks and an acceptable level of 
  accuracy was obtained.
\end{abstract}

\section{Introduction}
  We were tasked with picking a dataset and training a deep learning network. 
  First thing to do was to pick a dataset. Being an open-ended assignment there 
  was uncertainty as to what particular dataset to explore. Initial looks 
  involved different image classification datasets such as CIFAR-10, 
  Caltech 101, and NORB. Down the road there is no desire to work with image 
  data classification, work with files and datasets of continuous and 
  discrete data are preferred. After thorough search of the available datasets 
  it was decided pulsar classification best suited this paper.

  The last decision before pressing on to data format was to pick the correct 
  deep learning framework for the job. There were several options but TensorFlow 
  seemed like a good choice. Keras and PyTorch are other tools that utilize 
  TensorFlow but were not used because those are often considered a "front end" 
  for TensorFlow, which was not part of the goals of the assignment.

\section{Method}

\subsection{Data Format}
  After determining the dataset and the framework to be utilized it is 
  necessary to figure out how to read data from the dataset. A modular approach 
  was taken with this project. Users will be able to select a comma-separated 
  values (CSV) file to load in. By specifying a class to contain the CSV data it 
  is possible to run multiple datasets while making only minor modifications to 
  the code. The format is also much easier to read as a result of the class 
  format.

  Rather than code up a custom method of moving CSV data into a format usable by 
  the deep learning framework it was determined to "stand on the shoulders of 
  giants". Pandas was used to bring CSV data into usable form. After pulling the 
  data into a single structure it was necessary to split the data into training 
  and testing data. Again, rather than code that from scratch it was determined 
  best practice to utilize existing tools.

  For that endevour scikit-learn was used, specifically the 
  $train\_test\_split()$ method. As is standard for classification problems the 
  data was segmented into 80\% training and 20\% testing data. It was then 
  necessary to place the $class$ label into a data structure for later. For both 
  the train and test data, associated labels are passed, along with the data, 
  as tuples. The psuedocode for this section can be found under Algorithm 
  \ref{alg:input_fn}.

  \begin{algorithm}
    \caption{$input\_fn()$}
    \label{alg:input_fn}
    \begin{algorithmic}
      \STATE $data \gets CSV$\\
      \STATE $test, train \gets train\_test\_split(data)$
      \STATE $test\_label \gets test.pop(class)$
      \STATE $train\_label \gets train.pop(class)$
      \RETURN $(train, train\_label), (test,test\_label)$
    \end{algorithmic}
  \end{algorithm}

\section{Retrieval of style files}
